%*******************************************************
% Acknowledgments
%*******************************************************
\pdfbookmark[1]{Acknowledgements}{acknowledgements}

\bigskip

\begingroup
\let\clearpage\relax
\let\cleardoublepage\relax
\let\cleardoublepage\relax
\chapter*{Acknowledgements}

\def\thanks#1{%
\begingroup
\leftskip1em
\noindent #1
\par
\endgroup
}

I would like to cordially thank the following people who have assisted
me with priceless mentoring, support and suggestions throughout my doctoral study.

First, my sincere gratitude goes for Prof. Chih-Jen Shih who
offered me the opportunity to work in such a wonderful group. Coming
from the pure chemistry background, I received enormous mentoring and
advice from Prof. Shih to start my research in a chemical engineering
institute. 
%
I am  grateful to Dr. Elton Santos for accepting me doing the summer research exchange and bringing me into the fields of quantum chemistry and solid state physics.
%
I also want to thank Prof. Mathieu Luisier for his acceptance of being
my co-examiner.

Many thanks go to the Shih lab for being such a wonder place to work
in. As one of the first members in the group, I have witnessed the
expansion and success of this group, and have always enjoyed
discussing with everyone, not only about academic questions. I would
like to thank Sudhir, Wen-Yueh and Jakub for their generous help with
experiments. I would also thank Ruochen, Wan-Chi, Raja, Navanshu,
Franziska for their inputs into my research projects. In particular, I
thank Tommaso for his suggestive comments on many theoretical aspects,
and Anatol for teaching me \LaTeX{} and 3D graphics.


Many thanks to my collaborators, in particular to Dr. Roman Wyss,
Prof. Hyung Gyu Park (D-MAVT, ETH), Yen-Ying Lee, Prof. Yu-Cheng Chiu,
(NTUST, Taiwan), Prof. Shangchao Lin (SJTU, China), Prof. Chander
Sharma (IIT Ropar), Dr. Matija Varga (D-ITET, ETH) and Dr. Morteza
Aramesh (D-HEST, ETH).

Last but most importantly, I am always indebted to my wife Mingmin,
who has accompanied my throughout my PhD studies and give me constant
support. Any words won't be proper to describe my gratitude to you.

\endgroup
